---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# neopeptides

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![HitCount](http://hits.dwyl.io/ShixiangWang/neopeptides.svg)](http://hits.dwyl.io/ShixiangWang/neopeptides)
<!-- badges: end -->

The goal of **neopeptides** is to calculate and explore property indices of peptides for cancer immunotherapy study.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ShixiangWang/neopeptides")
```

### Configuration

To use neopeptide, `blast` is required.

After installation of `blast`, you can set the path with

```r
set_blast_path()
# e.g. 
# set_blast_path("/Users/wsx/anaconda3/bin/")
```

Then install required protein database with

```r
install_database()
```

## Available features

- `calc_geometric_mean()` - Calculate the Geometric Mean.
- `calc_harmonic_mean()` - Calculate the Harmonic Mean.
- `calc_iedb_score()` - Calculate IEDB Score for Peptides.
- `calc_dissimilarity()` - Calculate Dissimilarity Value to Reference Proteome for Peptides.

## Examples

```{r}
library(neopeptides)

calc_iedb_score(c("MTEYKLVVVGAGDVGKSALTIQLIQNHFVDEYDP", "MTEYKLVVVG"))
calc_dissimilarity(c("MTEYKLVVVGAGDVGKSALTIQLIQNHFVDEYDP", "MTEYKLVVVG"))
```


## Citation

Revisiting neoantigen depletion signal in the untreated cancer genome.
Shixiang Wang, Xuan Wang, Tao Wu, Zaoke He, Huimin Li, Xiaoqin Sun, Xue-Song Liu
bioRxiv 2020.05.11.089540; doi: https://doi.org/10.1101/2020.05.11.089540

## LICENSE

MIT © 2019-2020 Shixiang Wang, Xue-Song Liu

The software is made available for non commercial research purposes only
under the [MIT](LICENSE.md). However, notwithstanding any provision of
the MIT License, the software currently may not be used for commercial
purposes without explicit written permission after contacting Shixiang
Wang <wangshx@shanghaitech.edu.cn> or Xue-Song Liu
<liuxs@shanghaitech.edu.cn>.

-----

**[Cancer Biology Group](https://github.com/XSLiuLab) @ShanghaiTech**

**Research group led by Xue-Song Liu in ShanghaiTech University**
